Title

### 2016-10-23 paper/paper.tex
PAPER: stuff

\title{Title goes here}
\author{Filippo Sestini \\ Vrije Universiteit Amsterdam \\ f.sestini@student.vu.nl \and
  Davide Dal Bianco \\ Vrije Universiteit Amsterdam \\ d.dalbianco@student.vu.nl}

@@

Most of aircraft are provided with ADB-S transmitter, which send continuosly
information about the status and the position of the aircraft to guarantee
better air traffic control. The messages are not encripted and, in most region,
this technology will become mandatory in 2020. For these reasons OpenSky network
was recently born\cite{opensky}.

OpenSky is an open source network that aggregates ADS-B messages collected by
volunteers around the globe. The dataset is accessible to everyone for
non-profit purposes and the data is provided in the raw format, in order to
perform research and statistics about air traffic. \\
However there are some limitation to the data. Only part of Europe has a good
coverage, which means there are many areas where is not yet possible to detect
airplanes informations. Furthermore messages are collected by volunteers and
there is not guarantee that antennas are working properly 24/7.

@@

The ADS-B standard defines different kinds of messages which are sent at
different frequencies:

@@

In addition to these messages, other emergencies, priority, capability,
navigation accuracy category, and operational modes messages could be
broadcasted.

\subsection{Routes detection}

A way to reduce the number of air routes is illustrated bt J. DeArmon.
The research showed that similar routes can be grouped to reduce the
number of path between a pair of airports thus decrease air traffic 
congestion\cite{routeclustering}. The same approach could be used to detect
standard routes where aircraft fly, given the departure and arrival airports.
The first prototype of this model has been developed to improve the air traffic
flow in the National Airspace System of the USA.

@@

Routes are represented by an ordered list of the geographical sectors where the
aircrafts transit. Prior to define the clustering algorithm, it is important to
define how to measure the distance between two different routes. Since each
sector is identified by a code, the string editing distance can be used to
measure the distance between two different routes. The distance is therefore
represented by the minimum number of operation -- insertion, deletion and
replacement -- to transform Route 1 into Route 2 or vice-versa. Different weight
can also be applied to different operations. The distance should not depend by
the length of the routes and for this reason it is then divided by the sum of
the lengths of the routes. The final result represent the percentage of
difference between the routes.

@@

Given a distance measure for each couple of routes, it is necessary to define a
clustering algorithm to group them. Many methods has been tried during the
research and the \textit{Leader algorithm} showed the best results. It proceed
as follows:

\begin{enumerate}
  \item A random route is assigned as leader of a new cluster;
  \item All the other routes which distance from the leader is less than a
  threshold are assigned to the cluster;
  \item Repeat the steps with the remaining routes until all routes are assigned
  to a cluster.
\end{enumerate}

@@

% TODO: How other work could be based on ours?

>>>>

\title{Title}
\author{Filippo Sestini \\ Vrije Universiteit Amsterdam \\ f.sestini@student.vu.nl \and
  Davide Dal Bianco \\ Vrije Universiteit Amsterdam \\ d.dalbianco@student.vu.nl}

@@

Most aircrafts have equipped with an ADB-S transmitter, with which they send
information about their status and the position continuously, to guarantee
better air traffic control. These messages are not encripted and, in most regions,
this technology will become mandatory in 2020. For these reasons OpenSky network
has been created \cite{opensky}.

OpenSky is an open source network that aggregates ADS-B messages collected by
volunteers around the globe. The dataset is accessible to everyone for
non-profit purposes and the data is provided in raw format, in order to
perform research and statistics about air traffic. \\
There are some limitation to the data that is collected by the network. Western
Europe is well, but only partially covered. In areas where coverage is spotty or
absent, it is not possible to detect complete airplanes informations.
Additionally, messages are collected by volunteers and there are no guarantees
about the reliability of the collected information.

@@

The ADS-B standard defines different kinds of messages which are sent at
different frequencies. Among those types, four are particularly useful to
extract information about airplanes and flights:

@@

\subsection{Route clustering}

The research led by J. DeArmon showed that similar routes can be grouped
together based on their similarity, and the result of this grouping can be used
to reduce the number of paths between a pair of airports, thus decreasing air
traffic congestion\cite{routeclustering}. The first prototype of this model has
been developed to improve the air traffic flow in the National Airspace System
of the USA.

@@

Routes are represented by an ordered list of the geographical sectors where the
aircrafts transit. Prior to devising the clustering algorithm, it is important to
define how to measure the distance between two different routes. Since each
sector is identified by a code, the string editing distance can be used to
measure the distance between two different routes. The distance is therefore
represented by the minimum number of operations -- insertion, deletion and
replacement -- to transform Route 1 into Route 2 or vice-versa. Different weights
can also be applied to different operations. The distance should not depend by
the length of the routes and for this reason it is divided by the sum of
the lengths of the routes. The final result represents the percentage of
difference between the routes\cite{routeclustering}.

@@

Given a suitable distance measure for each couple of routes, it is necessary to
define a clustering algorithm to group them. Many methods have been tried during
the research described in \cite{routeclustering}, and the \textit{Leader
  algorithm} showed the best results. The algorithm proceeds by processing the
entire sequence of routes to be clustered, and it starts by assigning the first
of these routes to the first cluster. In then examines each route in turn: a
route that is sufficiently close to the leader of a cluster is assigned to it.
If no leader is found to be close enough to the current route, it is assigned as
the leader of a new cluster.

As it is explained in detail below, our route detection algorithm comprises a
part of route clustering that is inspired in many ways by the above algorithm,
as described in \cite{routeclustering}.

@@
